Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-26 Paper/ms.tex
Gliese 581 planets

The red dwarf star Gliese 581 is thought to host several planets. Exactly
how many is a matter of considerable debate. According to \citet{}, there
are two planets whose existence is not doubted, two more whose existence is
doubted by some, and another two thought not to exist by most groups.

@@

>>>>

The red dwarf star Gliese 581 is thought to host several planets. Exactly
how many is a matter of considerable debate. According to
\citet{2014Sci...345..440R}, there are two planets
(b and c, with periods 5.36 and 12.91 days respectively)
whose existence is generally
accepted, two more
(d and e, with periods 66 and 3.15 days respectively)
whose existence is mostly accepted, and another two
(f and g, with periods 433 and 36.5 days respectively)
whose existence is generally doubted.

@@

\bibitem[\protect\citeauthoryear{Robertson et 
al.}{2014}]{2014Sci...345..440R} Robertson P., Mahadevan S., Endl M., Roy 
A., 2014, Sci, 345, 440
